\REPLACEME{File 6\_Additional.tex}

\section{How to read this Specification}
\REPLACEME{A quick description of how to read this document, stating what it describes, and then what is in each section/clause.

Example:

This \textbf{specification} presents a metamodel for describing bird migration, Bird Land And Sea Tracking (BLAST).
Clauses 1 to 6 provide compliance rules, terms definitions and reference information.
Clause 7 provides the description of the metamodel for BLAST.
Clause 8 provides an informative example of how to use BLAST to track flock patterns.
Clause 9 provides informative examples of how to define individual routes in BLAST, with equivalent XML representations.}

All clauses of this document are normative unless explicitly marked ``(informative)''. The marking ``(informative)'' of a particular clause applies also to all contained sub-clauses of that clause.

\REPLACEME{To mark a clause (informative), follow the chapter, section, or subsection title with (informative), as in this Section.}

\section{Acknowledgments}
\REPLACEME{REQUIRED: Give formal acknowledgements here, starting with submitters and then working through contributors and supporters.  Delete either or both of the last two sections if there are no entries.}

The following organizations submitted this specification: 

\begin{itemize}
\item Company X
\item Company Y
\end{itemize}

The following organizations contributed to this specification: 

\begin{itemize}
\item Company A
\item Company B
\end{itemize}

The following organizations supported this specification: 

\begin{itemize}
\item Company 1
\item Company 2
\end{itemize}


%%% EXPERIMENTAL BELOW THIS POINT
% Go read sec 13.7 on conditionals *CAREFULLY*: http://mirrors.ibiblio.org/CTAN/info/texbytopic/TeXbyTopic.pdf
% % \newcommand{\Foo}[1]{#1}
% % \newcommand{\Bar}{A}

% % \ifthenelse{\equal{\Foo{A}}{\Bar}}{Same}{Not}

% \lengthETB\contributors

% % \ifthenelse{0=\expandafter\lengthETB\contributors}{Foo}{Bar}
% % \setvaluelist{\contributors}{{A}}
% \lengthETB{\contributors}

% \setvalue{\foo}{\lengthETB{\contributors}}
% \foo

% \ifstrequal{\lengthETB{\contributors}}{0}{Empty}{Not Empty}

% % \expandafter\ifstrequal\expandafter{\expandafter\expandafter\foo}{0}{Empty List}{Not empty list}


% % \ifthenelse{\value{\foo}=0}{Empty}{Not Empty}

% % \ifstrequal\foo0{Empty List}{Not empty list}

% % \expandafter\ifstrequal\expandafter{\foo}{0}{Empty List}{Not Empty List}

% % \setvalue{\foo}{\lengthETB{\contributors}}

% % \foo

% % \ifthenelse{\equal{\lengthETB{\contributors}}{0}}{Foo}{Bar}

% % \ifnum 0 = {\foo}{Foo}\else{Bar}\fi
\vfill\eject
